### 2014-06-24 tex/main-body-text.tex
few minor edits

\subsection*{Analysis of coastal California steelhead} 
To compare the behavior of {\sc flock} to that of {\sc structure} we used a published 
dataset of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci from \citet{Garzaetal_norcal}.  {\sc flock} 
was run six times using the default setting for all 
run parameters (initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0) for values of $K$ from 2 to 6. The stopping point of 
$K=6$ was chosen after four consecutive values of $K$
yielded no plateau (see below). For each value of $K$ from 2 to 6, the no-admixture, 
uncorrelated-allele-frequency model implemented in {\sc structure} was run 6 times using 
50,000 sweeps of burn-in followed by 150,000 sweeps of sample collection from the posterior. 
All runs were performed on a JNCS D685 with an i7 3.40GHz processor and 8GB
of RAM running 64-bit Windows 7. For each set of runs {\sc flock} reports the 
normalized likelihood values (the exponenetiated log-likelihood value for an individuals 
membership to each $K$ clusters scaled to sum to one) for the run that belongs to 
the longest plateau - the 'best run'. 
This value is comparable to the $q_i$ values
returned by {\sc structure}, which, in the no-admixture case, are posterior probabilities of cluster membership.
The program {\sc clumpp} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program {\sc district} \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

@@

\subsection*{Results} 
Run times were relatively short for both programs. {\sc flock} 
required 1133 minutes to complete all the runs, averaging 188.8 minutes for 
each of six groups of runs over $K$ from 2 to 6. {\sc structure} completed all the runs in 
486 minutes with each of the six groups of runs averaging 80.8 minutes. Increasing
$K$ from of 2 to 6 increased the run time for {\sc flock} by a factor of 2.4, while the run time 
for {\sc structure} increased by a factor of only 1.6.
\hrule

The allocation of indivividuals into K clusters was similar for each program. For all six groups 
of runs from \textit{k}=2-4, {\sc flock} lead to nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for \textit{k} of 2, two  
ended with identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). For all froups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed slightly. These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

>>>>

\subsection*{Analysis of coastal California steelhead} 
We used a published dataset of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci from \citet{Garzaetal_norcal} to compare the programs
{\sc flock} and {\sc structure} .  {\sc flock} 
was run six times using the default setting for all 
run parameters (initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0) for values of $K$ from 2 to 6. The stopping point of 
$K=6$ was chosen after four consecutive values of $K$
yielded no plateau (see below). For each value of $K$ from 2 to 6, the no-admixture, 
uncorrelated-allele-frequency model implemented in {\sc structure} was run 6 times with 
a 50,000 sweep burn-in followed by 150,000 sweep sample from the posterior. 
All runs were performed on a JNCS D685 with an i7 3.40GHz processor and 8GB
of RAM running 64-bit Windows 7. For each set of runs {\sc flock} reports the 
normalized likelihood values (the exponenetiated log-likelihood value for an individuals 
membership to each $K$ clusters scaled to sum to one) for the run that belongs to 
the longest plateau - the 'best run'. 
This value is comparable to the $q_i$ values
returned by {\sc structure}, which, in the no-admixture case, are posterior probabilities of cluster membership.
The program {\sc clumpp} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program {\sc district} \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

@@

\subsection*{Results} 
Run times were relatively short for both programs. {\sc flock} 
required 1133 minutes to complete all the runs, averaging 188.8 minutes for 
each of six groups of runs over $K$ from 2 to 6. All runs of {\sc structure} were completed in 
486 minutes. Each of the six groups of runs averaged 80.8 minutes. Increasing
$K$ from of 2 to 6 increased the run time for {\sc flock} by a factor of 2.4, while the run time 
for {\sc structure} increased by a factor of only 1.6.
\hrule

The allocation of indivividuals into K clusters was similar for each program. For all six groups 
of runs from \textit{k} = 2-4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for \textit{k} of 2, two  
runs yielded identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.
